### 2016-08-29 version0.0/intro0.01.tex
Applying M.D.'s comments on the intro.

\section{Prelude}
\label{sec: overview}
%what doIhave inside galaxies:
% stuffIdon't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas.
They all affect each others' formation, evolution, and extinction.
There is also dark matter inside every galaxy, which, to the best of our knowledge, only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their light.
Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
Therefore, by properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.

@@

The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state. 
The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
The energy of the anti-parallel mode is slightly less than the parallel mode.
Since atoms always want to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
The large amount of hydrogen atoms compensates for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
Observation of the \hi~atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.

@@

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

@@

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
Stellar mass determines the important properties of a star, such as luminosity, lifetime and its evolutionary path. 
One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar initial mass distribution of a star forming region.
Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
\cite{Salpeter55} empirically derived the stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
He introduced a power-law IMF $\Phi$  in the form:
\begin{equation}
\label{equ: salp}
\Phi (\log M) = dN / d \log M \propto M^{-\gamma }
\end{equation} 
where $M$ is the stellar mass, $\gamma$ is a power-law index, and $N$ is the number of stars in the logarithmic mass range of $\log M$ to $\log M + d\log M$.

@@

\subsubsection{Resolved Star Formation Indicators}
The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$~kpc of the Solar System. 
The number of YSOs can be converted to SFR using: 
\begin{equation}
SFR(YSO) = N_{yso} <M>/\tau 
\end{equation}
where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
$<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
$\tau$ is the lifetime of the YSO  $\tau \sim 2$~Myr~\citep{Evans09}. 
Since our current devices cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.

>>>>

\section{Prelude}
\label{sec: overview}
%what doIhave inside galaxies:
% stuffIdon't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are billions of stars, planets, and black holes, as well as dust and gas.
They all affect each others' formation, evolution, and extinction.
There is also dark matter inside every galaxy, which, to the best of our knowledge, only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their electromagnetic radiation.
Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
Therefore, with proper modeling of observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.

@@

The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state. 
The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
The energy of the anti-parallel mode is slightly less than the parallel mode.
Since atoms always tend to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
The large amount of hydrogen atoms compensates for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
Observation of the \hi~atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.

@@

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and empirically proven that they have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

@@

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
Stellar mass determines the important properties of a star, such as luminosity, lifetime and its evolutionary path. 
One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar initial mass distribution of a star forming region.
Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
\cite{Salpeter55} empirically described the stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
He introduced a power-law IMF $\Phi$  in the form:
\begin{equation}
\label{equ: salp}
\Phi (\log M) = dN / d \log M \propto M^{-\gamma }
\end{equation} 
where $M$ is the stellar mass, $\gamma$ is a power-law index, and $N$ is the number of stars in the logarithmic mass range of $\log M$ to $\log M + d\log M$.

@@

\subsubsection{Resolved Star Formation Indicators}
The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$~kpc of the Solar System. 
The number of YSOs can be converted to SFR using: 
\begin{equation}
\m {SFR}(YSO) = N_{yso} <M>/\tau 
\end{equation}
where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
$<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
$\tau$ is the lifetime of the YSO  $\tau \sim 2$~Myr~\citep{Evans09}. 
Since our current devices cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.
